---
title: "workflowr"
output: html_document
date: "2026-01-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

wflow_open("analysis/01-getting-started.Rmd")
```

getwd()
This semester, I plan to use some of the data I will use for my dissertation which includes data from two Networks in the US across between 7 and 9 sites. The data I will be tidying and exploring is data from parent reports on executive function and mental health in a cohort that is about half autistic and sex balanced. Because the ages of participants vary, some of the data is a little messy. 
```{r}
library(workflowr)


data <- read.csv("data/govdata.csv")


str(data)

```
Build site 
```{r}
wflow_build("analysis/01-getting-started.Rmd") # build only one script
wflow_build() # build the whole site
wflow_status() # check the build status

wflow_publish("analysis/01-getting-started.Rmd", message = "Add initial analysis page") # committing your work to the repository

wflow_publish("analysis/_site.yml") # committing your work to the repository

wflow_publish("analysis/index.Rmd", message = "Add initial analysis page") # committing your work to the repository

wflow_publish("analysis/about.Rmd", message = "Add initial analysis page") # committing your work to the repository

wflow_publish("analysis/license.Rmd", message = "Add initial analysis page") # committing your work to the repository

wflow_use_github("sonnyrussell")

wflow_git_push()
wflow_status()
```

